Mergeable Types

### 2017-02-27 paper/intro.tex
edits
fix wrapfig

\begin{wrapfigure}{l}{.5\textwidth}

@@

    \item We present a formalization of the \name programming model,
      and establish the comditions under which eventual convergence of
      concurrent version state can be guaranteed.

@@

The remainder of the paper is organized as follows.  We present the
\name\ programming model informally in the next section.
Sec.~\ref{sec:mergeable_types} develops a series of examples that
illustrate how merge operations can be defined and used.
Sec.~\ref{sec:formalization} defines an operational semantics, and
formalizes our intution of a mergeable type in terms of morphisms over
datatype operations.  We also present soundness (consistency) and
progress guarantees enjoyed by the
semantics. Sec.~\ref{sec:system-model} considers an instantiation of
the model suitable for distributed environments with network
partitions and failures.  Implementation details describing how we
incorporate mergeable types into OCaml are presented in
Sec.~\ref{sec:impl}.  Experimental results and benchmarks are given
in Sec.~\ref{sec:evaluation}.

, along with
a series of examples illustrating how merge operations can be defined
and used.  Sec.~\ref{sec:

>>>>

\begin{wrapfigure}{L}{.5\textwidth}

@@

    \item We present a formalization of the \name programming model,
      and establish the conditions under which eventual convergence of
      concurrent version state can be guaranteed.

@@

The remainder of the paper is organized as follows.  We present the
\name\ programming model informally in the next section.
Sec.~\ref{sec:mergeable_types} develops a series of examples that
illustrate how merge operations can be defined and used.
Sec.~\ref{sec:formalization} defines an operational semantics, and
formalizes our intution of a mergeable type in terms of morphisms over
datatype operations.  We also present soundness (consistency) and
progress guarantees enjoyed by the
semantics. Sec.~\ref{sec:system-model} considers an instantiation of
the model suitable for distributed environments with network
partitions and failures.  Implementation details describing how we
incorporate mergeable types into OCaml are presented in
Sec.~\ref{sec:impl}.  Experimental results and benchmarks are given in
Sec.~\ref{sec:evaluation}.  Secs.~\ref{sec:related}
and~\ref{sec:conclusions} describes related work and conclusions.
